\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{xcolor}

% Custom styling
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={SafeBox Technologies - L01 Team Roster},
    pdfpagemode=FullScreen,
}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[{\titlerule[0.5pt]}]
\titleformat{\subsection}{\normalfont\bfseries}{\thesubsection}{1em}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{S-VCG Funding Window 1: Evidence Document}} \\
    \vspace{0.2cm}
    {\large \textbf{L01 --- Student Team Roster \& Stipend Accounting}} \\
    \vspace{0.1cm}
    \rule{\linewidth}{1pt}
\end{center}

\vspace{0.2cm}

\section*{Document Control}
\begin{tabular}{ll}
    \textbf{Venture Name:} & SafeBox Technologies \\
    \textbf{Budget Line Item:} & L01 --- Personnel \& Stipends \\
    \textbf{Funding Window:} & Window 1 (Commercial Pilot Launch) \\
    \textbf{Total Stipend Budget:} & \text{₦}600,000 (3 Students $\times$ \text{₦}100,000 $\times$ 2 Months) \\
    \textbf{Date:} & June 16, 2026 \\
\end{tabular}

\vspace{0.5cm}

\section{Overview \& Compliance Statement}
In accordance with the S-VCG Window 1 guidelines, student stipends are capped at a maximum of \text{₦}100,000 per student per month for actively enrolled students contributing directly to the venture. 

SafeBox Technologies hereby submits the team roster of three (3) eligible students who will be working full-time during this two-month commercial pilot phase. All three individuals are currently enrolled in accredited higher education institutions and are responsible for the core engineering, system integration, and management of the pilot deployment.

\vspace{0.3cm}

\section{Eligible Student Team Summary}
The table below lists the registered student members, their roles, and their academic programs.

\renewcommand{\arraystretch}{1.3}
\begin{longtable}{p{0.25\linewidth} p{0.22\linewidth} p{0.38\linewidth} c}
    \toprule
    \textbf{Member} & \textbf{Role} & \textbf{Academic Programme \& Institution} & \textbf{Student?} \\
    \midrule
    \textbf{Engr. Abba Uba Sa'id} & Founder \& CEO & M.Sc. Electrical \& Computer Engineering, Carnegie Mellon University Africa & Yes \\
    \textbf{Abdullahi Ibrahim Salihu} & Team Lead / Systems Integrator & B.Eng. Electrical Engineering, Bayero University Kano & Yes \\
    \textbf{Mudassir Lawan} & Chief Engineer & B.Eng. Electrical Engineering, Bayero University Kano & Yes \\
    \bottomrule
\end{longtable}

\vspace{0.3cm}

\section{Detailed Member Profiles \& Pilot Responsibilities}

\subsection{Engr. Abba Uba Sa'id --- Founder \& CEO}
\begin{itemize}
    \item \textbf{Institution:} Carnegie Mellon University Africa (Kigali Innovation City, Rwanda)
    \item \textbf{Academic Program:} M.Sc. in Electrical and Computer Engineering (ECE)
    \item \textbf{Student ID / Matriculation Number:} CMUA-2025-ECE-0042 \textit{(Verify/Update)}
    \item \textbf{Role \& Responsibilities during Window 1 Pilot:}
        \begin{itemize}
            \item Overall project coordination, B2B partner relations (managing negotiations with GIG Logistics, Kano Line, and other corporate fleets).
            \item Backend server deployment and coordination of MQTT telematics connections (HiveMQ/EMQX configurations).
            \item Implementing the payment integration pipeline via Paystack to enable automated recurring subscription billing.
        \end{itemize}
\end{itemize}

\subsection{Abdullahi Ibrahim Salihu --- Team Lead / Systems Integrator}
\begin{itemize}
    \item \textbf{Institution:} Bayero University Kano (Kano, Nigeria)
    \item \textbf{Academic Program:} B.Eng. in Electrical Engineering
    \item \textbf{Student ID / Matriculation Number:} BUK/19/TEC/01042 \textit{(Verify/Update)}
    \item \textbf{Role \& Responsibilities during Window 1 Pilot:}
        \begin{itemize}
            \item Lead field systems integration and coordinate local installation processes on electric e-bikes and commercial vehicles.
            \item Developing and quality-testing custom wiring harnesses, SPDT Bosch relays, and valet switches for remote engine immobilization.
            \item Conducting field diagnostics, troubleshooting signal strength issues, and handling local customer onboarding training.
        \end{itemize}
\end{itemize}

\subsection{Mudassir Lawan --- Chief Engineer}
\begin{itemize}
    \item \textbf{Institution:} Bayero University Kano (Kano, Nigeria)
    \item \textbf{Academic Program:} B.Eng. in Electrical Engineering
    \item \textbf{Student ID / Matriculation Number:} BUK/19/TEC/00875 \textit{(Verify/Update)}
    \item \textbf{Role \& Responsibilities during Window 1 Pilot:}
        \begin{itemize}
            \item Firmware configuration and local flashing of Mokosmart VT001-L trackers.
            \item Development and implementation of the Bluetooth Passive Keyless Entry (PKE) bypass logic to pair the tracker with H1 BLE keychain fobs.
            \item Maintaining device configurations in the system database and monitoring device-to-cloud communications during pilot deployment.
        \end{itemize}
\end{itemize}

\vspace{0.5cm}
\rule{\linewidth}{0.5pt}
\vspace{0.2cm}

\begin{center}
    \textit{For any clarifications regarding this team roster, please contact SafeBox HQ at \href{mailto:safebox.hq@gmail.com}{safebox.hq@gmail.com} or +2347032101663.}
\end{center}

\end{document}
